### 2024-02-03 docs/projects/noj/ml.qmd
Noj - rerendered

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8908     -0.2103      0.0371      0.2256      0.8160

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0708     0.3356     6.1706     0.0000 ***
sepal-width         0.5954     0.0889     6.6968     0.0000 ***
petal-length        0.6671     0.0715     9.3273     0.0000 ***
petal-width        -0.4532     0.1618    -2.8002     0.0062 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3363 on 96 degrees of freedom
Multiple R-squared: 0.8299,    Adjusted R-squared: 0.8246
F-statistic: 156.1599 on 4 and 96 DF,  p-value: 8.448e-37

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8557     -0.1977      0.0083      0.1911      0.8454

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.0204     0.3078     6.5649     0.0000 ***
sepal-width         0.5955     0.0814     7.3147     0.0000 ***
petal-length        0.7028     0.0686    10.2518     0.0000 ***
petal-width        -0.5389     0.1507    -3.5765     0.0005 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3055 on 96 degrees of freedom
Multiple R-squared: 0.8637,    Adjusted R-squared: 0.8594
F-statistic: 202.7159 on 4 and 96 DF,  p-value: 2.121e-41
